Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
footnotes in Table 1

@@

@@

 \footnotetext[1]{The straight walks should morally correspond to some projective-injective objects in an exact category. We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.}
 \footnotetext[2]{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}

>>>>

	\begin{minipage}{18cm}
	\vspace*{-1cm}
	\noindent
	\renewcommand{\arraystretch}{1.2}

@@

	\renewcommand{\arraystretch}{1}
	\\[.2cm]
	\footnotemark[1]\footnotesize{The straight walks should morally correspond to some projective-injective objects in an exact category. We plan to further investigate the situation depicted in Figure~\ref{fig:exmAuslanderReitenQuiver}.} \\
	\footnotemark[2]\footnotesize{We do not know of an algebraic interpretation of the countercurrent order yet. We nonetheless included it in the table above since we think it might be of interest to find one.}
	\vspace*{.5cm}
	\end{minipage}

@@
